### 2021-05-04 yfcc100m/paper/vldb2021/eval.tex
Corrected figure 8 to use correct figure based on text, fixed minor errors

\subsection{Images Search}
\label{images}

@@

When considering Figure~\ref{fig:concurrency_comparison_q2}
through Figure~\ref{fig:concurrency_comparison_q4},
there are many reasons why we generally see performance improvement, the main being
that the entire operation (metadata query, image fetching and resizing) happens
on the server side in the case of VDMS, within a single message
exchange between the client and the server.
Many of the inefficiencies that come with combining tools that were designed
without visual data in mind simply disappear when building a tool that treats
visual entities as first class citizens, as it is the case of VDMS.
Another reason, which is quantifiable in the figures, is that
VDMS sends resized (smaller) versions to the client instead of the full image
to be resized on the client side (as is the case in the baselines).
This is in contrast with the baseline implementations,
where 2 rounds of blocking back-and-forth communication with the server is needed,
as depicted in Figure~\ref{fig:systems}.
Note that one could argue that the opposite will happen
when the resize operation retrieves a an up-sampled (larger) version of the image
instead of a down-sampled (smaller) one.
In practice, retrieving an up-sampled version is not a common use case,
given that up-sampling the image does not add any extra information that can help,
for instance, improve the accuracy of a ML model.
The case of down-sampling the original image is much more common and is the common
practice when it comes to image processing through CNNs \cite{cnn,resnet}.

@@

% \begin{figure}[ht]
% % WAS: begin{figure*}[ht]; textwidth
% \includegraphics[width=\columnwidth]{figures/plot_th_56_mosaic_results_throughput}
% \caption{Throughput Analysis using all queries from our use-case
% described in the Experimental Setup Section.
% We show queries in different figures for readability reasons.
% The experiments show the performance of all systems (VDMS and the two baselines) as the
% database size increases.
% These queries were run using 56 simultaneous clients,
% and averaged out of 10 runs.}
% \label{fig:q_throughput_56}
% \end{figure}

@@

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{figures/plot_th_16_mosaic_results_throughput}
\caption{Throughput Analysis using all queries from our use-case
described in the Experimental Setup Section.
We show queries in different figures for readability reasons.
The experiments show the performance of all systems (VDMS and the two baselines) as the
database size increases.
These queries were run using 16 simultaneous clients, and averaged out of 10 runs.}
\label{fig:q_throughput_16}
\end{figure}

@@

We designed VDMS with the idea in mind that pre-processing operations will be
commonly performed, as visual data is generally pre-processed before analytics
computation are performed on them.
Figure \ref{fig:q_throughput_56_resize} shows how the query throughput varies
when a pre-processing operations is applied (in this case, a resize operation).
The first thing to notice is that a resize operation is a significant part of
the overall operation (retrieval + preprocessing).
Doing a resize operation as part of the retrieval process
brings the throughput orders of magnitude down.
This is the case for both VDMS and the baseline.
Nonetheless, VDMS is orders of magnitude faster when retrieving images
both with and without resize operations.
An important thing to notice is that, even if a resized image is smaller,
and thus transfered faster between the server and the client,
transferring the image as is (without resize) is faster in this case.
This is a characteristic of the dataset, which has relatively small images
(the average image is about 150KB in size).
We have seen on other applications and datasets with higher resolution images
that transferring resized (or cropped) images is significantly faster than
transferring images as they are stored.
An interesting aspect to notice is that, when removing the resize operations,
differences between the 2 baseline systems become more noticeable.
For instance, for an image retrieval based on a single tag, we see how
\textit{postgresql} outperforms \textit{mysql}, but when adding geo-location
filtering, we see \textit{mysql} showing a small advantage.
When the resize operations is performed, both baselines do very similar
on 1tag based queries, and orders of magnitude worst than VDMS.
Note that in the baseline systems, the resize happens on the client side,
rather than on the server side.
This is the common case in most analytics applications, where pre-processing
operations happen on the client side (or when the analytics computation happens),
rather than near where the data is located, as it is the case with VDMS.
We kept both the server and client systems the same to avoid the computation
capabilities difference complicating our understanding of the results.

>>>>

\subsection{Image Search}
\label{images}

@@

When considering Figure~\ref{fig:concurrency_comparison_q2}
through Figure~\ref{fig:concurrency_comparison_q4},
there are many reasons why we generally see performance improvement, the main being
that the entire operation (metadata query, image fetching and resizing) happens
on the server side in the case of VDMS, within a single message
exchange between the client and the server.
Many of the inefficiencies that come with combining tools that were designed
without visual data in mind simply disappear when building a tool that treats
visual entities as first class citizens, as it is the case of VDMS.
Another reason, which is quantifiable in the figures, is that
VDMS sends resized (smaller) versions to the client instead of the full image
to be resized on the client side (as is the case in the baselines).
This is in contrast with the baseline implementations,
where 2 rounds of blocking back-and-forth communication with the server is needed,
as depicted in Figure~\ref{fig:systems}.
Note that one could argue that the opposite will happen
when the resize operation retrieves an up-sampled (larger) version of the image
instead of a down-sampled (smaller) one.
In practice, retrieving an up-sampled version is not a common use case,
given that up-sampling the image does not add any extra information that can help,
for instance, improve the accuracy of a ML model.
The case of down-sampling the original image is much more common and is the common
practice when it comes to image processing through CNNs \cite{cnn,resnet}.

@@

\begin{figure}[ht]
% WAS: begin{figure*}[ht]; textwidth
\includegraphics[width=\columnwidth]{figures/plot_th_56_mosaic_results_throughput}
\caption{Throughput Analysis using all queries from our use-case
described in the Experimental Setup Section.
We show queries in different figures for readability reasons.
The experiments show the performance of all systems (VDMS and the two baselines) as the
database size increases.
These queries were run using 56 simultaneous clients,
and averaged out of 10 runs.}
\label{fig:q_throughput_56}
\end{figure}

@@

% \begin{figure}[ht!]
% \includegraphics[width=\columnwidth]{figures/plot_th_16_mosaic_results_throughput}
% \caption{Throughput Analysis using all queries from our use-case
% described in the Experimental Setup Section.
% We show queries in different figures for readability reasons.
% The experiments show the performance of all systems (VDMS and the two baselines) as the
% database size increases.
% These queries were run using 16 simultaneous clients, and averaged out of 10 runs.}
% \label{fig:q_throughput_16}
% \end{figure}

@@

We designed VDMS with the idea in mind that pre-processing operations will be
commonly performed, as visual data is generally pre-processed before analytics
computation are performed on them.
Figure \ref{fig:q_throughput_56_resize} shows how the query throughput varies
when a pre-processing operations is applied (in this case, a resize operation).
The first thing to notice is that a resize operation is a significant part of
the overall operation (retrieval + preprocessing).
Doing a resize operation as part of the retrieval process
brings the throughput down by orders of magnitude.
This is the case for both VDMS and the baselines.
Nonetheless, VDMS is orders of magnitude faster when retrieving images
both with and without resize operations.
An important thing to notice is that, even if a resized image is smaller,
and thus transfered faster between the server and the client,
transferring the image as is (without resize) is faster in this case.
This is a characteristic of the dataset, which has relatively small images
(the average image is about 150KB in size).
We have seen on other applications and datasets with higher resolution images
that transferring resized (or cropped) images is significantly faster than
transferring images as they are stored.
An interesting aspect to notice is that, when removing the resize operations,
differences between the 2 baseline systems become more noticeable.
For instance, for an image retrieval based on a single tag, we see how
\textit{postgresql} outperforms \textit{mysql}, but when adding geo-location
filtering, we see \textit{mysql} showing a small advantage.
When the resize operations is performed, both baselines do very similar
on 1tag based queries, and orders of magnitude worst than VDMS.
Note that in the baseline systems, the resize happens on the client side,
rather than on the server side.
This is the common case in most analytics applications, where pre-processing
operations happen on the client side (or when the analytics computation happens),
rather than near where the data is located, as it is the case with VDMS.
We kept both the server and client systems the same to avoid the computation
capabilities difference complicating our understanding of the results.
